Software Development Methodology

### 2024-02-13 latex/ms.tex
.

\title{Development Methodology}

@@

\begin{abstract}
	This paper proposes a development methodology and also presents example use cases.
\end{abstract}

\section{Introduction}
Software development practices like agile~\cite{abrahamsson2017agile} are not concrete enough, thus multiple subversions of each of them exist in software development.
Loosely defined practices introduce non-portability issues between developers and through time, increasing development costs.

In this paper we present a development methodology which is concrete enough to be portable and abstract enough to be of general use.
We also present example use cases for python and tex document generation and website creation.

\section{Requirements}
POSIX utilities and shell are the base of any Unix system today.
However, they are not enough to cover modern user/developer requirements, such as machine learning and web applications.

@@

\section{Directory structure}
\dirtree{.0 python/|docs/|latex/.
.1 \texttt{.dockerignore}.
.1 \texttt{.gitignore}.
.1 Dockerfile.
.1 Makefile.
.1 main.py|index.html|ms.tex.
.1 prm/.
.1 pyproject.toml|package.json.
.1 tmp/.
}

The following directory structure is the superset of files and directories that the \texttt{python/} directory can consist.
The interface of the Makefile is a subset of the GNU standard targets.
File and directory name whitelisting is enforced with the target of having one file per `technology'.
\begin{itemize}
	\item \texttt{.dockerignore}: Consists of:
		\begin{itemize}
			\item * (every file/directory)
			\item except files needed for environment creation (e.g.\ \texttt{pyproject.toml})
		\end{itemize}
	\item \texttt{.gitignore}: Consists of:
		\begin{itemize}
			\item the temporary directory \texttt{tmp/} and
			\item the environmental variable file \texttt{.env}.
		\end{itemize}
	\item \texttt{Dockerfile}: Rarely editable. The developer edits:
		\begin{itemize}
			\item the FROM image and
			\item whether other apt-get installations are done.
		\end{itemize}
	\item \texttt{Makefile}: Non-editable. Properties~\cite{stallman1992gnu}:
		\begin{itemize}
			\item It should be POSIX-compliant and use POSIX utilities~\cite{lewine1991posix}.
			\item The \texttt{all} target should generate data saved in \texttt{tmp/}.
			\item The \texttt{check} target should check all \texttt{code}. It should also check and disallow any additional files or directories besides the ones defined here.
			\item The \texttt{clean} target should delete \texttt{tmp/}.
			\item It should support a \texttt{STAGING} environment variable which can be used for debugging purposes and having fast development iteration.
			\item It should create all files and directories from the structure if they do not already exist.
		\end{itemize}
	\item \texttt{main.py}: Frequently editable. The developer writes \texttt{code} in here that generates data saved in \texttt{tmp/}.
	\item \texttt{prm/}: The developer can place here all the files/directories for which generation from code is infeasible. It is a practical `backdoor' out of the file/directory name whitelisting of the Makefile. The contents of this directory should be as few as possible.
	\item \texttt{pyproject.toml}: Rarely editable. The developer edits:
		\begin{itemize}
			\item the dependencies and
			\item the version of the dependencies
		\end{itemize}
	\item \texttt{tmp/}: Data generated by \texttt{main.py} are saved here.
\end{itemize}

>>>>

\title{Software Development Methodology}

@@

\begin{abstract}
	We propose a portable and consistent software development methodology and also refer to example use cases.
\end{abstract}

\section{Introduction}
Code is usually targeted to be executed by multiple machines and developed by multiple humans.
Therefore, it is vital to have a portable way for machines to execute code and a consistent way for humans to develop code.
In this paper we present a simple software development methodology which satisfies these conditions.
We also refer example use cases for python machine learning applications, \LaTeX{} documents generation and web applications.

\section{Requirements}
Portable code execution is handled by:
\begin{itemize}
	\item POSIX Shell and Utilities
	\item Containers
\end{itemize}

POSIX is the base of all Unix-based systems today.
POSIX is maintained by the Austin Group.
However, they are not enough to cover modern user/developer requirements, such as machine learning and web applications.

@@

Code consistency is handled by:
\begin{itemize}
	\item applying a subset of the GNU standard targets for the interface of the Makefile.
	\item enforcing a directory structure.
\end{itemize}

\section{Directory structure}
The following directory structure is the superset of files and directories that the \texttt{python/} directory can consist.
File and directory name whitelisting is enforced with the target of having one file per `technology'.
\dirtree{.0 python/|docs/|latex/.
.1 \texttt{.dockerignore}.
.1 \texttt{.gitignore}.
.1 Dockerfile.
.1 Makefile.
.1 main.py|index.html|ms.tex.
.1 prm/.
.1 pyproject.toml|package.json.
.1 tmp/.
}

More specifically:
\begin{itemize}
	\item \texttt{.dockerignore}: Consists of:
		\begin{itemize}
			\item * (every file/directory)
			\item except files needed for environment creation (e.g.\ \texttt{pyproject.toml})
		\end{itemize}
	\item \texttt{.gitignore}: Consists of:
		\begin{itemize}
			\item the temporary directory \texttt{tmp/} and
			\item the environmental variable file \texttt{.env}.
		\end{itemize}
	\item \texttt{Dockerfile}: Rarely editable. The developer edits:
		\begin{itemize}
			\item the FROM image and
			\item whether other apt-get installations are done.
		\end{itemize}
	\item \texttt{Makefile}: Non-editable. Properties~\cite{stallman1992gnu}:
		\begin{itemize}
			\item It should be POSIX-compliant and use POSIX utilities~\cite{lewine1991posix}.
			\item The \texttt{all} target should generate data saved in \texttt{tmp/}.
			\item The \texttt{check} target should check all \texttt{code}. It should also check and disallow any additional files or directories besides the ones defined here.
			\item The \texttt{clean} target should delete \texttt{tmp/}.
			\item It should support a \texttt{STAGING} environment variable which can be used for debugging purposes and having fast development iteration.
			\item It should create all files and directories from the structure if they do not already exist.
		\end{itemize}
	\item \texttt{main.py}: Frequently editable. The developer writes \texttt{code} in here that generates data saved in \texttt{tmp/}.
	\item \texttt{prm/}: The developer can place here all the files/directories for which generation from code is infeasible. It is a practical `backdoor' out of the file/directory name whitelisting of the Makefile. The contents of this directory should be as few as possible.
	\item \texttt{pyproject.toml}: Rarely editable. The developer edits:
		\begin{itemize}
			\item the dependencies and
			\item the version of the dependencies
		\end{itemize}
	\item \texttt{tmp/}: Data generated by \texttt{main.py} are saved here.
\end{itemize}
